---
title: "NNbenchmark Ranking Function"
author: "All members of GSoC 2019 & 2020"
date: "2020/08/08"
output:
    html_document:
        toc: true
        toc_float: true
        number_sections: true
---

# Environment and datasets 

## Setup environment
```{r message=FALSE, warning=FALSE}
library(NNbenchmark)
library(kableExtra)
library(dplyr)   
library(stringr) 
options(scipen = 999)
if(dir.exists("D:/GSoC2020/Results/2020run04/"))
{  
  odir <- "D:/GSoC2020/Results/2020run04/"
}else
  odir <- "../results_2020_gsoc2020/"
```

# Read csv files and calculate some statistics for the metrics

```{r}
resultfile <- list.files(odir, pattern = "-results.csv", full.names = TRUE)

nonlargeresult <- grep("Wood", resultfile, invert = TRUE, value=TRUE)
lf   <- lapply(nonlargeresult, csv::as.csv)
names(lf) <- names(NNdatasets)
#lf <- lf[c(1:4,6,7,10,12)]
gfr <- lapply(lf, function(dfr) cbind(
					  ds   = str_remove(str_extract(dfr$event, "\\w+_"), "_"),
					  pfa  = str_sub(str_remove(dfr$event, str_extract(dfr$event, "\\w+_")),  1, -4),
					  run  = str_sub(dfr$event, -2, -1),
					  dfr[,c("RMSE","MAE","WAE","time")]
					  ))

yfr <- lapply(gfr, function(dfr) {
			as.data.frame(dfr %>%
			group_by(pfa) %>%
			summarise(time.mean = mean(time), 
			          RMSE.min = min(RMSE), 
			          RMSE.med = median(RMSE),
			          RMSE.d51 = median(RMSE) - min(RMSE),
			          MAE.med  = median(MAE),
			          WAE.med  = median(WAE)
					  )
			)})
yfr <- lapply(yfr, function(dfr) transform(dfr, npfa = 1:nrow(dfr)))
```

# Calculate ranks per datasets and merge results
```{r}
rankMOFtime <- function(dfr) {
	dfrtime <- dfr[order(dfr$time.mean),]
	dfrRMSE <- dfr[order(dfr$RMSE.min, dfr$time.mean, dfr$RMSE.med),]
	dfrRMSEmed  <- dfr[order(dfr$RMSE.med, dfr$RMSE.min, dfr$time.mean),]
	dfrRMSEd51  <- dfr[order(dfr$RMSE.d51),]
	dfrMAE      <- dfr[order(dfr$MAE.med),]
	dfrWAE      <- dfr[order(dfr$WAE.med),]
	transform(dfr, 
			  time.rank = order(dfrtime$npfa),
			  RMSE.rank = order(dfrRMSE$npfa),
			  RMSEmed.rank  = order(dfrRMSEmed$npfa),
			  RMSEd51.rank  = order(dfrRMSEd51$npfa),
			  MAE.rank = order(dfrMAE$npfa),
			  WAE.rank = order(dfrWAE$npfa)
			  )
}
sfr     <- lapply(yfr, rankMOFtime)
sfrwide <- do.call(cbind, sfr)
```

# Global scores on combined datasets (final table)
```{r}
sfr.time   <- sfrwide[, c(grep("time.rank", colnames(sfrwide)))]
time.score <- rank(apply(sfr.time, 1, sum), ties.method = "min")
sfr.RMSE       <- sfrwide[, c(grep("RMSE.rank", colnames(sfrwide)))]
RMSE.score     <- rank(apply(sfr.RMSE, 1, sum), ties.method = "min")
sfr.RMSEmed    <- sfrwide[, c(grep("RMSEmed.rank", colnames(sfrwide)))]
RMSEmed.score  <- rank(apply(sfr.RMSEmed, 1, sum), ties.method = "min")
sfr.RMSEd51    <- sfrwide[, c(grep("RMSEd51.rank", colnames(sfrwide)))]
RMSEd51.score  <- rank(apply(sfr.RMSEd51, 1, sum), ties.method = "min")
sfr.MAE       <- sfrwide[, c(grep("MAE.rank", colnames(sfrwide)))]
MAE.score     <- rank(apply(sfr.MAE, 1, sum), ties.method = "min")
sfr.WAE       <- sfrwide[, c(grep("WAE.rank", colnames(sfrwide)))]
WAE.score     <- rank(apply(sfr.WAE, 1, sum), ties.method = "min")

scoredfr0 <- data.frame(sfr$mDette[,"pfa",drop=FALSE], 
# scoredfr0 <- data.frame(sfr$uNeuroOne[,c("pfa")], 
						time.score, 
					    RMSE.score, 
					    RMSEmed.score,
					    RMSEd51.score,
              MAE.score,
              WAE.score)

scoredfr <- scoredfr0[order(scoredfr0$RMSE.score),]
rownames(scoredfr) <- NULL

kable(scoredfr)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

# Figures

## Some plots
```{r, fig.width=10}

plot(scoredfr[,c("time.score", "RMSE.score", "RMSEmed.score", "RMSEd51.score")], las = 1)


op <- par(mfrow = c(1,3), las = 1, mar = c(0,0.5,0,0.5), oma = c(2,2,3.5,2), cex = 1.1)
plot(scoredfr[,c("RMSE.score", "RMSEmed.score")]); abline(v=10.5, lty = 2)
mtext("x=RMSE.score,  y=RMSEmed.score", line = 1.5, font = 2)
plot(scoredfr[,c("RMSE.score", "time.score")], yaxt = "n"); abline(v=10.5, lty = 2)
mtext("x=RMSE.score,  y=time.score", line = 1.5, font = 2)
plot(scoredfr[,c("RMSE.score", "RMSEd51.score")], yaxt = "n"); Axis(scoredfr[,5], side = 4)
mtext("x=RMSE.score,  y=RMSEd51.score", line = 1.5, font = 2)
# mtext("(x=RMSE.score, y=RMSEmed.score)    (x=RMSE.score, y=time.score)    (x=RMSE.score, y=RMSEd51.score)", 
	  # outer = TRUE, line = 2, font = 2)
par(op)
```

## Comparison of global scores and RMSE value per dataset
```{r, fig.width=10, fig.height=15}
## =====================================
## GLOBAL SCORE APPLIED TO EVERY DATASET
## =====================================
merge_sfr_dfr <- function(x, y) {
	z <- cbind(
			x[,c("npfa","pfa","time.mean","RMSE.min","time.rank","RMSE.rank")], 
			y[,c("time.score","RMSE.score")]
		)
	z[order(z$RMSE.score),]
}
zfr <- lapply(sfr, merge_sfr_dfr, y = scoredfr0)
#str(zfr)
#str(sfr)

## =========================
## GRAPHIC RMSEscore_RMSEmin
## =========================
op <- par(mfrow = c(length(yfr)/2,2), las = 1, mar = c(0,4,0,0), oma = c(1,1,3,1))
for (j in seq_along(zfr)) {
names(zfr)[j]
plot(log1p(zfr[[j]][, "RMSE.score"]), log1p(zfr[[j]][, "RMSE.min"]),
     xlab = "RMSE.score (log1p)", ylab = "RMSE.min (log1p)", # main = names(zfr)[j], 
     las = 1, col = 0, xaxt = "n")
mtext(names(zfr)[j], line = -1.2, cex = 0.8)
text(log1p(zfr[[j]][, "RMSE.score"]), log1p(zfr[[j]][, "RMSE.min"]),
	 labels = zfr[[j]][, "RMSE.score"])
}
mtext("x=log1p(RMSE.score) (global)   y=log1p(RMSE.min) (per dataset)", outer = TRUE, line = 1)

op <- par(mfrow = c(length(yfr)/2,2), las = 1, mar = c(0,4,0,0), oma = c(1,1,3,1))
for (j in seq_along(zfr)) {
names(zfr)[j]
plot(zfr[[j]][, "RMSE.score"], zfr[[j]][, "RMSE.min"],
     xlab = "RMSE.score", ylab = "RMSE.min", # main = names(zfr)[j], 
     las = 1, col=0, xaxt = "n", pch=as.character(zfr[[j]][, "RMSE.score"]))
mtext(names(zfr)[j], line = -1.2, cex = 0.8)
text(zfr[[j]][, "RMSE.score"], zfr[[j]][, "RMSE.min"],
	 labels = zfr[[j]][, "RMSE.score"])

}
mtext("x=RMSE.score (global)   y=RMSE.min (per dataset)", outer = TRUE, line = 1)
```


## Comparison of global scores and time mean per dataset
```{r, fig.width=10, fig.height=15}

## ==============================
## GRAPHIC RMSEscore_timemean
## ==============================
op <- par(mfrow = c(length(yfr)/2,2), las = 1, mar = c(0,0,0,0), oma = c(1,1,3,1))
for (j in seq_along(zfr)) {
names(zfr)[j]
plot(log1p(zfr[[j]][, "RMSE.score"]), log1p(zfr[[j]][, "time.mean"]),
     xlab = "RMSE.score (log1p)", ylab = "time.mean (log1p)", 
     las = 1, col = 0, xaxt = "n", yaxt = "n")
mtext(names(zfr)[j], line = -1.2, cex = 0.8)
text(log1p(zfr[[j]][, "RMSE.score"]), log1p(zfr[[j]][, "time.mean"]),
	 labels = zfr[[j]][, "RMSE.score"])
}
mtext("x=log1p(RMSE.score) (global)   y=log1p(time.mean) (per dataset)", outer = TRUE, line = 1)


op <- par(mfrow = c(length(yfr)/2,2), las = 1, mar = c(0,4,0,0), oma = c(1,1,3,1))
for (j in seq_along(zfr)) {
names(zfr)[j]
plot(zfr[[j]][, "RMSE.score"], zfr[[j]][, "time.mean"],
     xlab = "RMSE.score", ylab = "time.mean", 
     las = 1, col = 0, xaxt = "n")
mtext(names(zfr)[j], line = -1.2, cex = 0.8)
text(zfr[[j]][, "RMSE.score"], zfr[[j]][, "time.mean"],
	 labels = zfr[[j]][, "RMSE.score"])
}
mtext("x=RMSE.score (global)   y=time.mean (per dataset)", outer = TRUE, line = 1)
```

## By different number of algorithms
```{r, fig.width=10, fig.height=15}
## =======================================
## GRAPHIC RMSEmin_timemean - 49 algos
## =======================================
op <- par(mfrow = c(length(yfr)/2,2), las = 1, mar = c(0,0,0,0), oma = c(1,1,3,1))
for (j in seq_along(zfr)) {
names(zfr)[j]
plot(log1p(zfr[[j]][, "RMSE.min"]), log1p(zfr[[j]][, "time.mean"]),
     xlab = "RMSE.min", ylab = "time.mean", #Â main = names(zfr)[j], 
     las = 1, col = 0, xaxt = "n", yaxt = "n")
mtext(names(zfr)[j], line = -1.2, cex = 0.8)
text(log1p(zfr[[j]][, "RMSE.min"]), log1p(zfr[[j]][, "time.mean"]),
	 labels = zfr[[j]][, "RMSE.score"])
}
mtext("x=RMSE.min (per dataset)   y=time.mean (per dataset)    49 algos", outer = TRUE, line = 1)


## =======================================
## GRAPHIC RMSEmin_timemean - 12 algos
## =======================================
op <- par(mfrow = c(length(yfr)/2,2), las = 1, mar = c(0,0,0,0), oma = c(1,1,3,1))
for (j in seq_along(zfr)) {
names(zfr)[j]
plot(log1p(zfr[[j]][1:12, "RMSE.min"]), log1p(zfr[[j]][1:12, "time.mean"]),
     xlab = "RMSE.min", ylab = "time.mean", #Â main = names(zfr)[j], 
     las = 1, col = 0, xaxt = "n", yaxt = "n")
mtext(names(zfr)[j], line = -1.2, cex = 0.8)
text(log1p(zfr[[j]][1:12, "RMSE.min"]), log1p(zfr[[j]][1:12, "time.mean"]),
	 labels = zfr[[j]][1:12, "RMSE.score"])
}
mtext("x=RMSE.min (per dataset)   y=time.mean (per dataset)    12 algos", outer = TRUE, line = 1)


## =======================================
## GRAPHIC RMSEmin_timemean - 09 algos
## =======================================
op <- par(mfrow = c(length(yfr)/2,2), las = 1, mar = c(0,0,0,0), oma = c(1,1,3,1))
for (j in seq_along(zfr)) {
names(zfr)[j]
plot(log1p(zfr[[j]][1:9, "RMSE.min"]), log1p(zfr[[j]][1:9, "time.mean"]),
     xlab = "RMSE.min", ylab = "time.mean", #Â main = names(zfr)[j], 
     las = 1, col = 0, xaxt = "n", yaxt = "n")
mtext(names(zfr)[j], line = -1.2, cex = 0.8)
text(log1p(zfr[[j]][1:9, "RMSE.min"]), log1p(zfr[[j]][1:9, "time.mean"]),
	 labels = zfr[[j]][1:9, "RMSE.score"])
}
mtext("x=RMSE.min (per dataset)   y=time.mean (per dataset)    9 algos", outer = TRUE, line = 1)

## THE END
## THE END


```



## Final graphics for article 
```{r, fig.width=10, fig.height=15}

myscore <- c(rep(2, 10), rep(1, NROW(zfr[[1]])-10))
myds <- seq_along(zfr)[names(zfr) %in% c("mIshigami", "uDreyfus1")]

png("mIshigami-uDreyfus1-RMSEmin.png", width = 1000, height = 500)
op <- par(mfrow = c(1,2), las = 1, mar = c(0,3,0,0), oma = c(1,1,3,2))
for (j in myds) {

plot(cumsum(myscore), zfr[[j]][, "RMSE.min"],
     xlab = "RMSE.score", ylab = "RMSE.min", 
     ylim=c(.9*min(zfr[[j]][, "RMSE.min"]), 1.1*max(zfr[[j]][, "RMSE.min"])),
     las = 1, col=0, xaxt = "n", pch=as.character(zfr[[j]][, "RMSE.score"]))
mtext(names(zfr)[j], line = -1.2, cex = 1.2)
text(cumsum(myscore), zfr[[j]][, "RMSE.min"],
	 labels = zfr[[j]][, "RMSE.score"])
grid()
}
mtext("RMSE.min (per dataset) against RMSE.score (global)", outer = TRUE, line = 1)
dev.off()

myscore <- c(rep(2, 10), rep(1, NROW(zfr[[1]])-30), rep(2, 20))
#myscore <- rep(2, NROW(zfr[[1]]))

png("mIshigami-uDreyfus1-timmean.png", width = 1000, height = 500)
op <- par(mfrow = c(1,2), las = 1, mar = c(0,3,0,0), oma = c(1,1,3,2))
for (j in myds) {
  
  #myscore <- rep(1, NROW(zfr[[j]]))
  #myscore[zfr[[j]][, "time.mean"] <= 0.5] <- 3

plot(cumsum(myscore), zfr[[j]][, "time.mean"],
     xlab = "RMSE.score", ylab = "time.mean", 
     ylim=c(.9*min(zfr[[j]][, "time.mean"]), 1.1*max(zfr[[j]][, "time.mean"])),
     las = 1, col=0, xaxt = "n", pch=as.character(zfr[[j]][, "RMSE.score"]))
mtext(names(zfr)[j], line = -1.2, cex = 1.2)
text(cumsum(myscore), zfr[[j]][, "time.mean"],
	 labels = zfr[[j]][, "RMSE.score"])
grid()
}
mtext("time.mean (per dataset) against RMSE.score (global)", outer = TRUE, line = 1)
dev.off()
```