---
title: "NNbenchmark Generic Function"
author: "All members of GSoC 2019 & 2020"
date: "2020/06/30"
output:
    html_document:
        toc: true
        toc_float: true
        number_sections: true
---

# Environment and datasets 

## Setup environment
```{r message=FALSE, warning=FALSE}
library(NNbenchmark)
library(kableExtra)
library(dplyr)   # for ranking section
library(stringr) # for ranking section
options(scipen = 999)
odir <- "D:/GSoC2020/Results/2020run01/"
```

## Datasets to test

```{r}
NNdataSummary(NNdatasets)
```

# Dedicated functions by packages


## brnn Train/predict Function - arguments x,y
```{r}
#library(brnn)
brnn.method <- "gaussNewton"
hyperParams.brnn <- function(optim_method, ...) {
    
    if (!is.element(optim_method, c("gaussNewton"))) stop("Invalid Parameters.")
    iter   <- 200
    
    params <- paste0("method=", optim_method, "_iter=", iter)
    
    out <- list(iter = iter, params = params)
    
    return (out)
}
NNtrain.brnn <- function(x, y, dataxy, formula, neur, optim_method, hyperParams,...) {
    
    hyper_params <- do.call(hyperParams.brnn, list(brnn.method))
    
    iter <- hyper_params$iter
    
    NNreg <- brnn::brnn(x, y, neur, normalize = FALSE, epochs = iter, verbose = FALSE)
    
    return (NNreg)
}
NNpredict.brnn <- function(object, x, ...)
    predict(object, x)
NNclose.brnn <- function()
  if("package:brnn" %in% search())
    detach("package:brnn", unload=TRUE)
brnn.prepareZZ <- list(xdmv = "m", ydmv = "v", zdm = "d", scale = TRUE)
if(FALSE)
res <- trainPredict_1data(1, brnn.method, "NNtrain.brnn", "hyperParams.brnn", "NNpredict.brnn", 
                               NNsummary, "NNclose.brnn", NA, brnn.prepareZZ, nrep=5, echo=TRUE, doplot=FALSE,
                               pkgname="brnn", pkgfun="brnn", csvfile=TRUE, rdafile=TRUE, odir=odir)
```

## CaDENCE Train/predict Function - arguments x,y
```{r}
#library(CaDENCE)
CaDENCE.method <- c("optim", "psoptim", "Rprop")
hyperParams.CaDENCE <- function(optim_method, ...) {
  
    if (optim_method == "optim")    {iter <- 200} 
    if (optim_method == "psoptim")  {iter <- 1000}
    if (optim_method == "Rprop")    {iter <- 1000}
  
    params <- paste0("method=", optim_method, "_iter=", iter)
    
    out <- list(iter = iter, method = optim_method, params = params, maxit.Nelder=1)
    return (out)
}

NNtrain.CaDENCE <- function(x, y, dataxy, formula, neur, optim_method, hyperParams,...) {
    
    hyper_params <- do.call(hyperParams, list(optim_method, ...))
    
    iter <- hyper_params$iter
    method <- hyper_params$method

    NNreg <- CaDENCE::cadence.fit(x = x, y = y, 
                                iter.max = iter, 
                                n.hidden = neur, 
                                hidden.fcn = tanh, 
                                method = method, 
                                n.trials = 1, 
                                trace = 0, 
                                maxit.Nelder = 1, 
                                f.cost = cadence.cost,
                                distribution = list(density.fcn = dnorm,
                                                    parameters = c("mean", "sd"),
                                                    parameters.fixed = NULL,
                                                    output.fcns = c(identity, exp)))
    return (NNreg)
}
NNpredict.CaDENCE <- function(object, x, ...)
    CaDENCE::cadence.predict(x = x, fit = object)[,1]
NNclose.CaDENCE <- function()
  if("package:CaDENCE" %in% search())
    detach("package:CaDENCE", unload=TRUE)
CaDENCE.prepareZZ <- list(xdmv = "m", ydmv = "m", zdm = "d", scale = TRUE)

if(FALSE)
res <- trainPredict_1data(1, CaDENCE.method, "NNtrain.CaDENCE", "hyperParams.CaDENCE", "NNpredict.CaDENCE", 
                               NNsummary, "NNclose.CaDENCE", NA, CaDENCE.prepareZZ, nrep=2, echo=TRUE, doplot=FALSE,
                               pkgname="CaDENCE", pkgfun="cadence.fit", csvfile=TRUE, rdafile=TRUE, odir=odir)
```


## MachineShop Train/predict Functions - arguments formula,data
```{r}
#library(MachineShop)
MachineShop.method <- "none"
hyperParams.MachineShop <- function(...) {
    return (list(iter=200, trace=FALSE, linout=TRUE))
}
NNtrain.MachineShop <- function(x, y, dataxy, formula, neur, method, hyperParams, ...) {
    
    hyper_params <- do.call(hyperParams, list(...))
    trace <- hyper_params$trace
    maxit <- hyper_params$iter
    linout <- hyper_params$linout #linearoutpputunit
    myNN <- MachineShop::NNetModel(size = neur, linout = linout, maxit = maxit,
                                   trace=trace)
    MachineShop::fit(formula, data = dataxy, model = myNN)
    
}
NNpredict.MachineShop <- function(object, x, ...)
    as.numeric(predict(object, newdata=x, type="response"))
NNclose.MachineShop <- function()
  if("package:MachineShop" %in% search())
    detach("package:MachineShop", unload=TRUE)
MachineShop.prepareZZ <- list(xdmv = "m", ydmv = "m", zdm = "d", scale = TRUE)
if(FALSE)
res <- trainPredict_1data(1, MachineShop.method, "NNtrain.MachineShop", "hyperParams.MachineShop", "NNpredict.MachineShop", 
                               NNsummary, "NNclose.MachineShop", NA, MachineShop.prepareZZ, nrep=5,
                               echo=TRUE, doplot=FALSE, echoreport=0,
                               pkgname="MachineShop", pkgfun="fit", csvfile=TRUE, rdafile=TRUE, odir=odir)
    
```


## minpack.lm train/predict functions - arguments formula,data
```{r}
#library(minpack.lm)
minpack.lm.method <- "none"
hyperParams.minpack.lm <- function(...) {
    return (list(iter=200, sdnormstart=0.1))
}
NNtrain.minpack.lm <- function(x, y, dataxy, formula, neur, method, hyperParams, NNfullformula, NNparam, ...) {
    
    hyper_params <- do.call(hyperParams, list(...))
    
    start <- round(rnorm(NNparam, sd = hyper_params$sdnormstart), 4)
    names(start)  <- paste0("b", 1:NNparam)
    minpack.lm::nlsLM(NNfullformula, data = dataxy, start=start,
                      control = list(maxiter = hyper_params$iter))
}
NNpredict.minpack.lm <- function(object, x, ...)
  predict(object, newdata=as.data.frame(x))
NNclose.minpack.lm <- function()
  if("package:minpack.lm" %in% search())
    detach("package:minpack.lm", unload=TRUE)
minpack.lm.prepareZZ <- list(xdmv = "m", ydmv = "v", zdm = "d", scale = TRUE)
if(FALSE)
res <- trainPredict_1data(1, minpack.lm.method, "NNtrain.minpack.lm", "hyperParams.minpack.lm", "NNpredict.minpack.lm", 
                               NNsummary, "NNclose.minpack.lm", NA, minpack.lm.prepareZZ, nrep=5,
                               echo=TRUE, doplot=FALSE, echoreport=0,
                               pkgname="minpack.lm", pkgfun="nlsLM", csvfile=TRUE, rdafile=TRUE, odir=odir)
```


## monmlp train/predict functions - arguments x,y
```{r}
#library(monmlp)
monmlp.method <- c("BFGS", "Nelder-Mead")
hyperParams.monmlp <- function(...) {
    return (list(iter=200, silent=TRUE, scale=TRUE))
}
NNtrain.monmlp <- function(x, y, dataxy, formula, neur, method, hyperParams, ...) {
    
    hyper_params <- do.call(hyperParams, list(...))
    
    monmlp::monmlp.fit(x, y, hidden1 = neur, scale.y = hyper_params$scale, silent=hyper_params$silent,
                         method = method, iter.max = hyper_params$iter)
}
NNpredict.monmlp <- function(object, x, ...)
  as.numeric(monmlp::monmlp.predict(x, weights=object))
NNclose.monmlp <- function()
  if("package:monmlp" %in% search())
    detach("package:monmlp", unload=TRUE)
monmlp.prepareZZ <- list(xdmv = "m", ydmv = "m", zdm = "d", scale = TRUE)
if(FALSE)
res <- trainPredict_1data(1, monmlp.method, "NNtrain.monmlp", "hyperParams.monmlp", "NNpredict.monmlp", 
                               NNsummary, "NNclose.monmlp", NA, monmlp.prepareZZ, nrep=2,
                               echo=TRUE, doplot=FALSE, echoreport=0,
                               pkgname="monmlp", pkgfun="monmlp.fit", csvfile=TRUE, rdafile=TRUE, odir=odir)
```


## nlsr train/predict functions - arguments formula,data
```{r}
#library(nlsr)
nlsr.method <- "none"
hyperParams.nlsr <- function(...) {
    return (list(iter=200, sdnormstart=0.1))
}
NNtrain.nlsr <- function(x, y, dataxy, formula, neur, method, hyperParams, NNfullformula, NNparam, ...) {
    
    hyper_params <- do.call(hyperParams, list(...))
    
    start <- round(rnorm(NNparam, sd = hyper_params$sdnormstart), 4)
    names(start)  <- paste0("b", 1:NNparam)
    
    nlsr::nlxb(NNfullformula, start = start, data = dataxy,
                                control = list(femax = hyper_params$iter))
}
NNpredict.nlsr <- function(object, x, ...)
  as.numeric(predict(object, x))
NNclose.nlsr <- function()
  if("package:nlsr" %in% search())
    detach("package:nlsr", unload=TRUE)
nlsr.prepareZZ <- list(xdmv = "d", ydmv = "v", zdm = "d", scale = TRUE)
if(FALSE)
res <- trainPredict_1data(1, nlsr.method, "NNtrain.nlsr", "hyperParams.nlsr", "NNpredict.nlsr", 
                               NNsummary, "NNclose.nlsr", NA, nlsr.prepareZZ, nrep=5,
                               echo=TRUE, doplot=FALSE, echoreport=0,
                               pkgname="nlsr", pkgfun="nlxb", csvfile=TRUE, rdafile=TRUE, odir=odir)
```



## nnet Train/predict Functions - arguments x,y
```{r}
#library(nnet)
nnet.method <- "none"
hyperParams.nnet <- function(...) {
    return (list(iter=200, trace=FALSE))
}
NNtrain.nnet <- function(x, y, dataxy, formula, neur, method, hyperParams, ...) {
    
    hyper_params <- do.call(hyperParams, list(...))
    
    nnet::nnet(x, y, size = neur, linout = TRUE, maxit = hyper_params$iter, trace=hyper_params$trace)
}
NNpredict.nnet <- function(object, x, ...)
    predict(object, newdata=x)
NNclose.nnet <- function()
  if("package:nnet" %in% search())
    detach("package:nnet", unload=TRUE)
nnet.prepareZZ <- list(xdmv = "d", ydmv = "v", zdm = "d", scale = TRUE)
if(FALSE)
res <- trainPredict_1data(1, nnet.method, "NNtrain.nnet", "hyperParams.nnet", "NNpredict.nnet", 
                               NNsummary, "NNclose.nnet", NA, nnet.prepareZZ, nrep=5, echo=TRUE, doplot=FALSE,
                               pkgname="nnet", pkgfun="nnet", csvfile=TRUE, rdafile=TRUE, odir=odir)
    
```


## qrnn Train/predict Function - arguments x,y
```{r}
#library(qrnn)
qrnn.method <- "none"
hyperParams.qrnn <- function(optim_method, ...) {
    
    maxiter <- 200
    init.range = c(-0.1, 0.1, -0.1, 0.1)
    params <- paste0("method=", optim_method, "_iter=", maxiter)
  
    out <- list(iter = maxiter, params = params, init.range=init.range)
    return (out)
}
NNtrain.qrnn <- function(x, y, dataxy, formula, neur, optim_method, hyperParams,...) {
    
    hyper_params <- do.call(hyperParams, list(optim_method, ...))
    
    NNreg <- qrnn::qrnn.fit(x, y, n.hidden = neur, 
                     iter.max = hyper_params$iter, n.trials = 1,
                     init.range = hyper_params$init.range, trace=FALSE)
    
    return (NNreg)
}
NNpredict.qrnn <- function(object, x, ...)
  qrnn::qrnn.predict(x, object)
NNclose.qrnn <- function()
  if("package:qrnn" %in% search())
    detach("package:qrnn", unload=TRUE)
qrnn.prepareZZ <- list(xdmv = "m", ydmv = "m", zdm = "d", scale = TRUE)
if(FALSE)
res <- trainPredict_1data(1, qrnn.method, "NNtrain.qrnn", "hyperParams.qrnn", "NNpredict.qrnn", 
                               NNsummary, "NNclose.qrnn", NA, qrnn.prepareZZ, nrep=5, echo=TRUE, doplot=FALSE,
                               pkgname="qrnn", pkgfun="qrnn.fit", csvfile=TRUE, rdafile=TRUE, odir=odir)
```


## radiant.model Train/predict Functions - arguments xy,y
```{r}
#library(radiant.model)
radiant.model.method <- "none"
hyperParams.radiant.model <- function(...) {
    return (list(type="regression", decay=0))
}
NNtrain.radiant.model <- function(x, y, dataxy, formula, neur, method, hyperParams, ...) {
    
    hyper_params <- do.call(hyperParams, list(...))
    
    radiant.model::nn(dataxy, rvar = "y", evar = attr(terms(formula), "term.labels"),
                      type = hyper_params$type, size = neur, 
                      decay = hyper_params$decay)
    
}
NNpredict.radiant.model <- function(object, x, ...)
   predict(object, pred_data=as.data.frame(x))$Prediction
NNclose.radiant.model <- function()
  if("package:radiant.model" %in% search())
    detach("package:radiant.model", unload=TRUE)
radiant.model.prepareZZ <- list(xdmv = "m", ydmv = "m", zdm = "d", scale = TRUE)
if(FALSE)
res <- trainPredict_1data(1, radiant.model.method, "NNtrain.radiant.model", "hyperParams.radiant.model", "NNpredict.radiant.model", 
                               NNsummary, "NNclose.radiant.model", NA, radiant.model.prepareZZ, nrep=5,
                               echo=TRUE, doplot=FALSE, echoreport=0,
                               pkgname="radiant.model", pkgfun="nn", csvfile=TRUE, rdafile=TRUE, odir=odir)
    
```


## rminer Train/predict Functions - arguments formula,data
```{r}
#library(rminer)
rminer.method <- "none"
hyperParams.rminer <- function(...) {
    return (list(task="reg", iter=200))
}
NNtrain.rminer <- function(x, y, dataxy, formula, neur, method, hyperParams, ...) {
    
    hyper_params <- do.call(hyperParams, list(...))
    
    rminer::fit(formula, data = dataxy, model = "mlp", task = hyper_params$task, 
                                        size = neur, maxit = hyper_params$iter)
}
NNpredict.rminer <- function(object, x, ...)
   as.numeric(rminer::predict(object, newdata=as.data.frame(x)))
NNclose.rminer <- function()
  if("package:rminer" %in% search())
    detach("package:rminer", unload=TRUE)
rminer.prepareZZ <- list(xdmv = "m", ydmv = "m", zdm = "d", scale = TRUE)
if(FALSE)
res <- trainPredict_1data(1, rminer.method, "NNtrain.rminer", "hyperParams.rminer", "NNpredict.rminer", 
                               NNsummary, "NNclose.rminer", NA, rminer.prepareZZ, nrep=2,
                               echo=TRUE, doplot=FALSE, echoreport=0,
                               pkgname="rminer", pkgfun="fit", csvfile=TRUE, rdafile=TRUE, odir=odir)
```


## RSNNS Train/predict Function - arguments x,y
```{r}
#library(RSNNS)
RSNNS.method <- c("Rprop","BackpropBatch","BackpropChunk","BackpropMomentum",
                  "BackpropWeightDecay","Quickprop","SCG","Std_Backpropagation")
hyperParams.RSNNS <- function(optim_method, ...) {
    
    if(optim_method %in% c("Rprop","BackpropChunk","BackpropMomentum","BackpropWeightDecay","SCG","Std_Backpropagation"))
      maxiter <- 1000
    else
      maxiter <- 10000
    
    params <- paste0("method=", optim_method, "_iter=", maxiter)
  
    out <- list(iter = maxiter, sdnormstart=0.1)
    return (out)
}
NNtrain.RSNNS <- function(x, y, dataxy, formula, neur, optim_method, hyperParams, NNfullformula, NNparam,...) {
    
    hyper_params <- do.call(hyperParams, list(optim_method, ...))
    
    start <- round(rnorm(NNparam, sd = hyper_params$sdnormstart), 4)
    names(start)  <- paste0("b", 1:NNparam)
    
    NNreg <- RSNNS::mlp(x, y, initFuncParams = start,
                 size = neur, learnFunc = optim_method, 
                 maxit = hyper_params$iter, linOut = TRUE)
    
    return (NNreg)
}
NNpredict.RSNNS <- function(object, x, ...)
  predict(object, x)
NNclose.RSNNS <- function()
  if("package:RSNNS" %in% search())
    detach("package:RSNNS", unload=TRUE)
RSNNS.prepareZZ <- list(xdmv = "m", ydmv = "m", zdm = "d", scale = TRUE)
if(FALSE)
res <- trainPredict_1data(1, RSNNS.method, "NNtrain.RSNNS", "hyperParams.RSNNS", "NNpredict.RSNNS", 
                               NNsummary, "NNclose.RSNNS", NA, RSNNS.prepareZZ, nrep=5, echo=TRUE, doplot=FALSE,
                               pkgname="RSNNS", pkgfun="mlp", csvfile=TRUE, rdafile=TRUE, odir=odir)
```

## validann Train/predict Function - arguments x,y
```{r}
#library(validann)
validann.method <- c("Nelder-Mead", "BFGS", "CG", "L-BFGS-B", "SANN")
hyperParams.validann <- function(optim_method, ...) {
    
    if (optim_method == "Nelder-Mead")  {maxiter <- 10000} 
    if (optim_method == "BFGS")         {maxiter <- 200}
    if (optim_method == "CG")           {maxiter <- 1000}
    if (optim_method == "L-BFGS-B")     {maxiter <- 200}
    if (optim_method == "SANN")         {maxiter <- 10000}
    
    params <- paste0("method=", optim_method, "_iter=", maxiter)
  
    out <- list(iter = maxiter, method = optim_method, params)
    return (out)
}
NNtrain.validann <- function(x, y, dataxy, formula, neur, optim_method, hyperParams, NNfullformula, NNparam,...) {
    
    hyper_params <- do.call(hyperParams, list(optim_method, ...))
    
    iter <- hyper_params$iter
    method <- hyper_params$method
    
    NNreg <- validann::ann(x, y, size = neur, 
                           method = method, maxit = iter)
    
    return (NNreg)
}
NNpredict.validann <- function(object, x, ...)
  predict(object, x)
NNclose.validann <- function()
  if("package:validann" %in% search())
    detach("package:validann", unload=TRUE)
validann.prepareZZ <- list(xdmv = "m", ydmv = "m", zdm = "d", scale = TRUE)
if(FALSE)
res <- trainPredict_1data(1, validann.method, "NNtrain.validann", "hyperParams.validann", "NNpredict.validann", 
                               NNsummary, "NNclose.validann", NA, validann.prepareZZ, nrep=5, echo=TRUE, doplot=FALSE,
                               pkgname="validann", pkgfun="ann", csvfile=TRUE, rdafile=TRUE, odir=odir)
```

# Launch all packages

```{r All, message=FALSE, warning=FALSE}
methodlist <- list(brnn.method, 
                   CaDENCE.method[1], 
                   MachineShop.method, 
                   minpack.lm.method, 
                   monmlp.method[1],
                   nlsr.method, 
                   nnet.method, 
                   qrnn.method,
                   radiant.model.method,
                   rminer.method,
                   validann.method[c(2,4)])
pkgfunmat <- rbind(c("brnn", "brnn"),
                   c("CaDENCE", "cadence.fit"),
                   c("MachineShop", "fit"),
                   c("minpack.lm", "nlsLM"),
                   c("monmlp", "monmlp.fit"),
                   c("nlsr", "nlxb"),
                   c("nnet", "nnet"),
                   c("qrnn", "qrnn.fit"),
                   c("radiant.model", "nn"),
                   c("rminer", "fit"),
                   c("validann","ann"))
colnames(pkgfunmat) <- c("pkg", "fun")  
trainvect <- paste("NNtrain", pkgfunmat[,"pkg"], sep=".")
hypervect <- paste("hyperParams", pkgfunmat[,"pkg"], sep=".")
predvect <- paste("NNpredict", pkgfunmat[,"pkg"], sep=".")
#close function is only needed for h2o
closevect <- paste("NNclose", pkgfunmat[,"pkg"], sep=".")
startvect <- rep(NA, length(pkgfunmat[,"pkg"]))
startvect[pkgfunmat[,"pkg"] == "h2o"] <- "NNstart.h2o"
preparelist <- list(brnn.prepareZZ, 
                   CaDENCE.prepareZZ, 
                   MachineShop.prepareZZ, 
                   minpack.lm.prepareZZ, 
                   monmlp.prepareZZ,
                   nlsr.prepareZZ, 
                   nnet.prepareZZ, 
                   qrnn.prepareZZ,
                   radiant.model.prepareZZ,
                   rminer.prepareZZ,
                   validann.prepareZZ)
names(preparelist) <- pkgfunmat[,"pkg"]
#print(cbind(pkgfunmat, startvect))

resall <- lapply(1:12, function(i)
  trainPredict_1data(dset=i, method=methodlist, train=trainvect, hyper=hypervect,
                     pred=predvect, summary=NNsummary, close=closevect, 
                     start=startvect, prepare=preparelist, nrep=20, echo=TRUE, doplot=TRUE,
                     pkgname=pkgfunmat[,"pkg"], pkgfun=pkgfunmat[,"fun"], csvfile=TRUE, rdafile=TRUE, odir=odir))



kable(ht(resall))
```

# Ranking

## Read csv files and calculate some statistics for the metrics

```{r}
setwd(odir) ; getwd()
lf        <- lapply(list.files(odir, pattern = "-results.csv", full.names = TRUE), csv::as.csv)
names(lf) <- names(NNdatasets)
lf <- lf[c(1:5,7,11,12)] #selecting multivariate datasets, uDmod1, uDreyfus1, uGauss3, and uNeuroOne
ht(lf)
gfr <- lapply(lf, function(dfr) cbind(
					  ds   = str_remove(str_extract(dfr$event, "\\w+_"), "_"),
					  pfa  = str_sub(str_remove(dfr$event, str_extract(dfr$event, "\\w+_")),  1, -4),
					  run  = str_sub(dfr$event, -2, -1),
					  dfr[,c("RMSE","MAE","WAE","time")]
					  ))

yfr <- lapply(gfr, function(dfr) {
			as.data.frame(dfr %>%
			group_by(pfa) %>%
			summarise(time.mean = mean(time), 
			          RMSE.min = min(RMSE), 
			          RMSE.med = median(RMSE),
			          RMSE.d51 = median(RMSE) - min(RMSE),
			          MAE.med  = median(MAE),
			          WAE.med  = median(WAE)
					  )
			)})
yfr <- lapply(yfr, function(dfr) transform(dfr, npfa = 1:nrow(dfr)))
ht9(yfr)
```

## Calculate ranks per datasets and merge results
```{r}
rankMOFtime <- function(dfr) {
	dfrtime <- dfr[order(dfr$time.mean),]
	dfrRMSE <- dfr[order(dfr$RMSE.min, dfr$time.mean, dfr$RMSE.med),]
	dfrRMSEmed  <- dfr[order(dfr$RMSE.med, dfr$RMSE.min, dfr$time.mean),]
	dfrRMSEd51  <- dfr[order(dfr$RMSE.d51),]
	dfrMAE      <- dfr[order(dfr$MAE.med),]
	dfrWAE      <- dfr[order(dfr$WAE.med),]
	transform(dfr, 
			  time.rank = order(dfrtime$npfa),
			  RMSE.rank = order(dfrRMSE$npfa),
			  RMSEmed.rank  = order(dfrRMSEmed$npfa),
			  RMSEd51.rank  = order(dfrRMSEd51$npfa),
			  MAE.rank = order(dfrMAE$npfa),
			  WAE.rank = order(dfrWAE$npfa)
			  )
}
sfr     <- lapply(yfr, rankMOFtime); sfr
sfrwide <- do.call(cbind, sfr); sfrwide
sfrwide[, grep("pfa", colnames(sfrwide))] # Identical columns
```

## Global scores on combined datasets
```{r}
sfr.time   <- sfrwide[, c(grep("time.rank", colnames(sfrwide)))]
time.score <- rank(apply(sfr.time, 1, sum), ties.method = "min")
sfr.RMSE       <- sfrwide[, c(grep("RMSE.rank", colnames(sfrwide)))]
RMSE.score     <- rank(apply(sfr.RMSE, 1, sum), ties.method = "min")
sfr.RMSEmed    <- sfrwide[, c(grep("RMSEmed.rank", colnames(sfrwide)))]
RMSEmed.score  <- rank(apply(sfr.RMSEmed, 1, sum), ties.method = "min")
sfr.RMSEd51    <- sfrwide[, c(grep("RMSEd51.rank", colnames(sfrwide)))]
RMSEd51.score  <- rank(apply(sfr.RMSEd51, 1, sum), ties.method = "min")
sfr.MAE       <- sfrwide[, c(grep("MAE.rank", colnames(sfrwide)))]
MAE.score     <- rank(apply(sfr.MAE, 1, sum), ties.method = "min")
sfr.WAE       <- sfrwide[, c(grep("WAE.rank", colnames(sfrwide)))]
WAE.score     <- rank(apply(sfr.WAE, 1, sum), ties.method = "min")

scoredfr0 <- data.frame(sfr$uNeuroOne[,"pfa",drop=FALSE], 
# scoredfr0 <- data.frame(sfr$uNeuroOne[,c("pfa")], 
						time.score, 
					    RMSE.score, 
					    RMSEmed.score,
					    RMSEd51.score,
              MAE.score,
              WAE.score)

scoredfr <- scoredfr0[order(scoredfr0$RMSE.score),]
rownames(scoredfr) <- NULL

kable(scoredfr)
```
